---
title: "Data simulation and parameters recovery with brms"
output:
  html_document:
    self_contained: true
    toc: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE
)
```


```{r setup}
#| message: false

library(osfHYoungFFCWS)
library(tidybayes)
library(dplyr)
```




## Baseline model



### Data simulation

**Formulas used for data simulation with `lavaan::simulateData()`:**

```{r}
gen_model_formula(model_type = "baseline")
```

**Histograms for the simulated dataset:**

```{r}
#| message: false

df_baseline <- targets::tar_read(sim_data_baseline)
hist_sim(df_baseline)
```


### Recovery of model parameters

#### Mean estimates

```{r}
mod_baseline <- targets::tar_read(fit_baseline)
check_params_recovery(mod_baseline, model_type = "baseline") |>
    flextable::flextable() |>
    flextable::set_header_labels(values = list(
        Estimate = "mean estimate",
        simu = "simulation coefficient"
    )) |>
    flextable::set_caption("Estimated regression coefficients compared to
                            the values used for the simulation.") |>
    flextable::width(width = 2.5)
```

#### Posterior distributions

```{r}
#| warning: false

plot_posteriors(mod_baseline, "std", model_type = "baseline",
    plot_title = "Baseline model - predictors of short-term deliberation")
```

```{r}
#| warning: false

plot_posteriors(mod_baseline, "internalizing", model_type = "baseline",
    plot_title = "Baseline model - predictors of internalizing symptoms")
```

```{r}
#| warning: false

plot_posteriors(mod_baseline, "externalizing", model_type = "baseline",
    plot_title = "Baseline model - predictors of externalizing symptoms")
```




## Mediation model



### Data simulation

**Formulas used for data simulation with `lavaan::simulateData()`:**

```{r}
gen_model_formula(model_type = "mediation")
```

**Histograms for the simulated dataset:**

```{r}
#| message: false

df_mediation <- targets::tar_read(sim_data_mediation)
hist_sim(df_mediation)
```


### Recovery of model parameters

#### Mean estimates

```{r}
mod_mediation <- targets::tar_read(fit_mediation)
check_params_recovery(mod_mediation, model_type = "mediation") |>
    flextable::flextable() |>
    flextable::set_header_labels(values = list(
        Estimate = "mean estimate",
        simu = "simulation coefficient"
    )) |>
    flextable::set_caption("Estimated regression coefficients compared to
                            the values used for the simulation.") |>
    flextable::width(width = 2.5)
```

#### Posterior distributions

```{r}
#| warning: false

plot_posteriors(mod_mediation, "std", model_type = "mediation",
    plot_title = "Mediation model - predictors of short-term deliberation")
```

```{r}
#| warning: false

plot_posteriors(mod_mediation, "repro", model_type = "mediation",
    plot_title = "Mediation model - predictors of reproductive effort")
```

```{r}
#| warning: false

plot_posteriors(mod_mediation, "internalizing", model_type = "mediation",
    plot_title = "Mediation model - predictors of internalizing symptoms")
```

```{r}
#| warning: false

plot_posteriors(mod_mediation, "externalizing", model_type = "mediation",
    plot_title = "Mediation model - predictors of externalizing symptoms")
```




## Moderation model



### Data simulation

**Formulas used for data simulation with `lavaan::simulateData()`:**

```{r}
gen_model_formula(model_type = "moderation")
```

**Histograms for the simulated dataset:**

```{r}
#| message: false

df_moderation <- targets::tar_read(sim_data_moderation)
hist_sim(df_moderation)
```


### Recovery of model parameters

#### Mean estimates

```{r}
mod_moderation <- targets::tar_read(fit_moderation)
check_params_recovery(mod_moderation, model_type = "moderation") |>
    flextable::flextable() |>
    flextable::set_header_labels(values = list(
        Estimate = "mean estimate",
        simu = "simulation coefficient"
    )) |>
    flextable::set_caption("Estimated regression coefficients compared to
                            the values used for the simulation.") |>
    flextable::width(width = 2.5)
```

#### Posterior distributions

```{r}
#| warning: false

plot_posteriors(mod_moderation, "std", model_type = "moderation",
    plot_title = "Moderation model - predictors of short-term deliberation")
```

```{r}
#| warning: false

plot_posteriors(mod_moderation, "repro", model_type = "moderation",
    plot_title = "Moderation model - predictors of reproductive effort")
```

```{r}
#| warning: false

plot_posteriors(mod_moderation, "internalizing", model_type = "moderation",
    plot_title = "Moderation model - predictors of internalizing symptoms")
```

```{r}
#| warning: false

plot_posteriors(mod_moderation, "externalizing", model_type = "moderation",
    plot_title = "Moderation model - predictors of externalizing symptoms")
```
