---
title: "osf-demo-pipeline"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

Below we provide an overview of the main functions from this package that are
used in the demonstration pipeline. To see the output of the demonstration
pipeline refer to this
[article](/articles/Data-simulation-and-parameter-recovery-with-brms.html).
Recall also from the instructions in the
[README](/index.html)
that the files that define the `targets` pipeline can be obtained with
`osfHYoungFFCWS::gen_targets_script()`.

We start by loading the package into our R environment:

```{r setup}
library(osfHYoungFFCWS)
```

The first step of the pipeline consists in simulating datasets with all the
variables used in each of the three types of path models (baseline, mediation
and moderation models).

The values used by default for the simulation are based on the associations
found between the variables of interest in previous studies. They can be
inspected with a call to `get_params_simu()`:

```r
get_params_simu(model_type = "<baseline|mediation|moderation>")
```

Overriding this default values can be achieved simply by providing a new
vector of values to the `set_params_simu()` function:

```r
set_params_simu(x, model_type = "<baseline|mediation|moderation>")
# here x is a numeric vector of length equal to the number of path coefficients
# for the chosen type of model 
```

As an example, to change the strength of the association between short-term
deliberation and externalizing symptoms for the baseline model to a new value
of 0.45 (standardized coefficient), we would run the following commands:

```r
# we first assign the default values to a new vector
coeffs <- get_params_simu(model_type = "baseline")
# we then modify the values for the relationship(s) of interest
coeffs["externalizing ~ std"] <- 0.45
# we use the new list of coefficients to update the simulation parameters
set_params_simu(coeffs, model_type = "baseline")
```

Generating datasets for specific path models using the default package values
or values set by the user can be done with the `simulate_dataset()` function:

```r
simulate_dataset(model_type = "<baseline|mediation|moderation>")
```

The `hist_sim(<dataset>)` function can be used to quickly plot histograms for all the
variables in the dataset.

Once we have simulated datasets, we can use the `brms_fit()` function to
estimate the associated path models with brms:

```r
brms_fit(<simulated dataset>, model_type = "<baseline|mediation|moderation>")
```

With brms fit objects obtained, we can now check whether our bayesian estimation
procedure was able to recover the values used as simulation parameters. This can
be done by generating a table where each row correspond to the path model
coefficient for a given relationship and the columns give respectively the
mean of the posterior distribution and the target value used for the
simulation. The function `check_params_recovery()` will produce such a table:

```r
check_params_recovery(<model fit>, model_type = "<baseline|mediation|moderation>") |>
```

However, richer information can be obtained by plotting the full posterior
distributions for all the relationships estimated in the path model. For
instance, to assess the parameter recovery for the mediation model, we would
run the following commands:

```r
# %#% Mediation model

# posterior distributions for the predictors of short-term deliberation
plot_posteriors(mod_mediation, "std", model_type = "mediation",
    plot_title = "Mediation model - predictors of short-term deliberation")

# posterior distributions for the predictors of reproductive efforts
plot_posteriors(mod_mediation, "repro", model_type = "mediation",
    plot_title = "Mediation model - predictors of reproductive effort")

# posterior distributions for the predictors of internalizing symptoms
plot_posteriors(mod_mediation, "internalizing", model_type = "mediation",
    plot_title = "Mediation model - predictors of internalizing symptoms")

# posterior distributions for the predictors of externalizing symptoms
plot_posteriors(mod_mediation, "externalizing", model_type = "mediation",
    plot_title = "Mediation model - predictors of externalizing symptoms")
```

The graphs created by `plot_posteriors()` will show in addition to the
posterior distribution the target value used in the simulation as a vertical
line, as well as the mean of the posterior (black dot), 66% and 95% credible
intervals (black horizontal segments). See the
[article](/articles/Data-simulation-and-parameter-recovery-with-brms.html)
with the output of the demonstration pipeline for examples.

